% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,10pt]{article}
% \usepackage[a4paper, top=1in, bottom=1in, left=1in, right=1in]{geometry}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% Use Times New Roman
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
% \usepackage{mathptmx} % Times New Roman

% Uncomment the next line to use Arial instead
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}
\setlength{\baselineskip}{15pt} % spacing between lines
% \setlength{\lineskip}{5pt}      % additional spacing between lines
\usepackage{enumitem} % For customizing lists

% Set spacing between items in itemize environment
\setlist[itemize]{itemsep=3pt} % Adjust the length as needed
% \setlist[itemize]{topsep=1pt} % Adjust the length as needed

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
% Custom \section
\definecolor{MyBlue}{RGB}{69, 66, 254}
\definecolor{bullets}{RGB}{89, 89, 89}
\titleformat{\section}{\normalfont\large\bfseries\raggedright}{}{0em}{}[{\color{gray!40}\titlerule[0.8pt]}]
\titlespacing{\section}{0pt}{4pt}{5pt}


%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}
\usepackage{soul} % for more flexible underlining



%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\definecolor{blackcolour}{rgb}{0,0,0}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}
\usepackage{ragged2e} % Load the ragged2e package
%debug page outer frames
%\usepackage{showframe}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

% Setup hyperref package, and colors for links
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\definecolor{blackcolour}{rgb}{0,0,0}
\hypersetup{
    colorlinks,
    breaklinks,
    urlcolor=linkcolour,
    linkcolor=linkcolour
}
%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\hypersetup{urlcolor=blackcolour, linkcolor=blackcolour}
\begin{tabularx}{\linewidth}{@{} C @{}}
{\textbf{\Huge{OMTEJA YALLAPRAGADA}}} \\[7.5pt]
\href{tel:+916305700243}{+91 6305700243} \ $|$ \ 
\href{mailto:yallapragadaomteja@gmail.com}{yallapragadaomteja@gmail.com}\ $|$ \ 
\href{https://linkedin.com/in/omteja}{linkedin.com/in/omteja} \ $|$ \
\href{https://github.com/omteja04}{github.com/omteja04}  \\
% \href{https://omteja04.github.io}{\raisebox{-0.05\height}\faGlobe \ my-portfolio} \\[2pt] 
% \hypersetup{urlcolor=blackcolour, linkcolor=blackcolour}
\end{tabularx} 

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------
% \section{Summary}
% \begin{tabularx}{\linewidth}{@{}X @{}}	
%     Innovative \textbf{Software Engineer} with a solid foundation in \textbf{programming}, \textbf{problem-solving}. Proficient in multiple \textbf{programming languages} and \textbf{development tools}, interested in \textbf{Web Development} and currently learning  \textbf{AWS Cloud Development}. Eager to collaborate with cross-functional teams to deliver innovative products. Seeking opportunities to apply and expand skills in dynamic environments.
% \end{tabularx}



%	EDUCATION
%----------------------------------------------------------------------------------------

\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
2022 --- Present & B.Tech. (C.S.E) at \textbf{Aditya College of Engineering and Technology}  \hfill \textcolor{Gray} \hfill \normalsize CGPA: 8.43 \\

2022 & Class 12th, Andhra Pradesh State Board \hfill 95.3\% \\
% 2020 & Class 10th, Andhra Pradesh State Board \hfill (100\%) 
\end{tabularx}  \\[-0.4em]


%	SKILLS
%----------------------------------------------------------------------------------------
\section{Tech Stack}
\begin{tabularx}{\linewidth}{@{}l X@{}}
\textbf{Core} & \textcolor{bullets}{Data Structures, Algorithms, OOP, DBMS} \\
\textbf{Programming Languages} & \textcolor{bullets}{C / C++, Java, Python} \\
\textbf{Front-End Tools} & \textcolor{bullets}{HTML5, CSS3, JavaScript} \\
\textbf{Databases} & \textcolor{bullets}{MySQL} \\
\textbf{System Skills} & \textcolor{bullets}{Linux} \\
\textbf{Developer Tools} & \textcolor{bullets}{Git, GitHub, Markdown, REST APIs, Figma}  \\
\textbf{Technologies} & \textcolor{bullets}{AWS Cloud Development}  \\[-0.2em]


\end{tabularx}
% \vspace{-0.4em} % Reduce space before the next section
%Projects
%----------------------------------------------------------------------------------------
\section{Projects}
\begin{tabularx}{\linewidth}{ @{} X  @{} }
    \textbf{My-Portfolio - An Interactive Resume Website} \hfill \href{https://omteja04.github.io/}{\underline{Live Demo}}  \ $|$ \ \href{https://github.com/omteja04/omteja04.github.io}{\underline{Source Code}}  \\[-0.3em]
    \begin{itemize}
        \item \textcolor{bullets}{Developed a responsive portfolio website ensuring compatibility across various screen sizes and devices.}
        \item \textcolor{bullets}{Created an interactive platform where users can download my resume, view projects \& explore earned certifications.}
        \item {HTML5, CSS3, JavaScript}
    \end{itemize} \\
    
    \textbf{Sushi-Shinobi - A Front-end Landing Page} \hfill \href{https://sushi-shinobi.vercel.app/}{\underline{Live Demo}}  \ $|$ \ \href{https://github.com/omteja04/sushi-shinobi}{\underline{Source Code}}  \\[-0.3em]
    \begin{itemize}
        \item \textcolor{bullets}{Developed a comprehensive and user-friendly landing page of a restaurant with impressive performance in all devices.}
        \item \textcolor{bullets}{Implemented smooth scroll animations significantly enhancing the user experience by adding interactive elements.}
        \item {HTML5, CSS3, JavaScript library --- AOS (Animate On Scroll)}
    \end{itemize} \\
    \textbf{levi.ly - URL Shortener} \hfill \href{https://omteja04.github.io/levi}{\underline{Live Demo}}  \ $|$ \ \href{https://github.com/omteja04/levi}{\underline{Source Code}}  \\[-0.3em]
    \begin{itemize}
        \item \textcolor{bullets}{Designed and Built a Serverless URL Shortener featuring a simple user-friendly web interface, which efficiently converts long URLs into shortened links.}
        \item \textcolor{bullets}{Although the project has been temporarily deactivated to manage costs, it can be reactivated for demonstrations.}
        \item AWS Lambda, DynamoDB, API Gateway, JavaScript, HTML, CSS.
    \end{itemize} \\
    
    \textbf{Inventory Management System - Java Based Application} \hfill\href{https://github.com/omteja04/InventoryManagementSystem}{\underline{Source Code}}  \\[-0.3em]
    \begin{itemize}
        \item \textcolor{bullets}{Built a Java application utilizing Java Database Connectivity and GUI frameworks for managing inventory operations.}
        \item \textcolor{bullets}{Focused on adding, deleting, and organizing the inventory.}
        \item {JDBC, Java GUI Frameworks --- SWING, AWT, Database --- MySQL}
    \end{itemize}
    
\end{tabularx}


%Internships
%---------------------------------------------------------------------------------------
\section{Internships}
\begin{tabularx}{\linewidth}{ @{} X @{} }
\textbf{AWS Cloud Development Intern} \hfill (May 2024 – July 2024) \\
\small \textbf{Technical Hub} --- \emph{provides training aligned with certifications} \\[-0.3em]
    \begin{itemize}
       \item \textcolor{bullets}{Learned AWS Cloud fundamentals and development concepts.}
       \item \textcolor{bullets}{Enhanced understanding and gained hands-on experience with a range of AWS services, including Amazon EC2, AWS Lambda, Amazon S3, and DynamoDB.}
        % \item  {\textbf{Postman API Fundamentals Student Expert}} 
        \item \textcolor{bullets}{Earned the } \href{https://rb.gy/yomey5}{\textbf{Postman API Fundamentals Student Expert}} \textcolor{bullets}{ badge for expertise in API development and testing.}

    \end{itemize} 
\end{tabularx}

\vspace{-0.9em} % Reduce space before the next section
%---------------------------------------------------------------------------------------
\section{Competency}
\begin{tabularx}{\linewidth}{@{} X@{}}	
    \textbf{LeetCode:} Successfully Solved \textbf{500+ Problems}, Max. Contest Rating \textbf{1667*} \hfill \href{https://www.leetcode.com/omteja04}{\underline{omteja04}} \\
    \textbf{GeeksforGeeks:} Solved \textbf{400+ problems}, \textbf{Campus Rank 131}, Max. Contest Rating \textbf{1789*} \hfill \href{https://www.geeksforgeeks.org/user/omteja04/}{\underline{omteja04}} \\
    \textbf{Codeforces:} \textbf{Newbie}, Max. Contest  Rating \textbf{1127*}
    \hfill  \href{https://codeforces.com/profile/omteja04}{\underline{omteja04}} \\
    \textbf{CodeChef:} \textbf{2 Star}, Max. Contest Rating \textbf{1462*} \hfill \href{https://www.codechef.com/users/omteja04}{\underline{omteja04}} \\
    \textbf{HackerRank:} \textbf{5 Star} in Data Structures and Algorithms, C, C++, Java, Python \hfill \href{https://www.hackerrank.com/profile/omteja04}{\underline{omteja04}} \\
\end{tabularx}
%-----------------------------------------------------------------------------------------------
\section{Certifications}
\begin{tabularx}{\linewidth}{@{} l X@{}}
    \href{https://rhtapps.redhat.com/verify?certId=240-110-783}{\textbf{Red Hat Certified System Administrator}} (RHCSA) & \textcolor{bullets}{\emph{Red Hat}} \\
    IT Specialist in \href{https://www.credly.com/badges/aea2b491-a0e3-4ed8-8e4b-2da4ec311639/public_url}{\textbf{HTML \& CSS}}, \href{https://www.credly.com/badges/17ee233e-54bd-4955-94a4-999a9468809f/public_url}{\textbf{JAVA}} &  \textcolor{bullets}{\emph{Certiport Pearson}}
\end{tabularx}
% \hypersetup{urlcolor=blackcolour, linkcolor=blackcolour}
%--------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\vfill

\end{document}
